MoneyBallR_Modeling

### 2019-09-24 hw1/results/moneyballr_stepwise_model_corey.rmd
Added set.seed to make it reproducible

```{r}
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
```

@@

# Stepwise Regression
```{r}
train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]

>>>>

```{r}
set.seed(1234)
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
```

@@

# Stepwise Regression
```{r}
set.seed(1234)
train.index1 <- createDataPartition(df_train$TARGET_WINS, p = .7, list = FALSE)
train_data<- df_train[ train.index1,]
hold_out_data  <- df_train[-train.index1,]
